First question from data request:
1. Does atypical perceptual processing track with reduced cognitive and social functioning?
2. Which social and cognitive functioning variables best predict atypical task performance?
3. Does accounting for cognitive/social functioning significantly reduce group differences?

So atypical perception is:
1. Ebbinghaus -> context_sensitivity, misleading_index, helpful_index (don't know what 2sd is yet)
2. Mooney -> Silverstein's paper from 2021 seems largely focused on upright_percent_reported 
and inverted_percent_reported

Cognitive functioning is: 
1. the Wide Range Achievement Test (WRAT) -> wrat_standardscore
2. the Brief Assessment of Cognition in Schizophrenia-Symbol Coding (BACS) -> bacs_total
3. Hopkins Verbal Learning Test-Revised (HVLT-R) -> hvlt

Social functioning is Global Functioning Scale:
1. Social and Role (GFS-S/R) -> gfs_current, gfr_current
2. Social Phobia Scale ->sps_total



so let's load data
```{r}
library(data.table)
main_dir = "/Users/victorpokorny/Library/CloudStorage/GoogleDrive-vpokorny123@gmail.com/My Drive/CAPR Ebbinghaus and Mooney/"
load(paste0(main_dir,'RData/fixed_upright_faces_data.RData'))
source(paste0(main_dir,'R_scripts/funcs.R')) # big group of functions
```

let's look at hists and scatterplots of key variables
starting with Ebbinghaus
```{r}
hist(main_df$helpful_index)
hist(main_df$misleading_index)
hist(main_df$context_sensitivity)
scatterplot(main_df$context_sensitivity, main_df$helpful_index)
scatterplot(main_df$context_sensitivity, main_df$misleading_index)
scatterplot(main_df$helpful_index, main_df$misleading_index)
#ok so helpful and misleading aren't strongly correlated with each other, but both are 
#strongly correlate with the difference score (which makes sense)
```

next let's look at Mooney
```{r}
hist(main_df$upright_faces_reported) 
hist(main_df$inverted_faces_reported) 
sum(!is.na(main_df$inverted_faces_reported))
sum(!is.na(main_df$upright_faces_reported))

#shouldn't there be a max of 43 responses?
#let's get rid of folks with more than 43 upright or inverted responses
main_df$upright_faces_reported[main_df$upright_faces_reported>43] <- NA
main_df$inverted_faces_reported[main_df$inverted_faces_reported>43] <- NA
hist(main_df$upright_faces_reported) 
hist(main_df$upright_percent_reported) 
hist(main_df$upright_percent_reported_adjusted) 
hist(main_df$inverted_faces_reported) 

#phew so hopefully we've sufficiently cleaned these data
scatterplot(main_df$upright_faces_reported,main_df$inverted_faces_reported)

```
now let's look at social variables... 
```{r}
hist(main_df$gfr_current) # ceiling effect here as well
hist(main_df$gfs_current) # bit of a ceiling effect here it would seem
scatterplot(main_df$gfr_current,main_df$gfs_current ) #apparent range restriction here

#how about sps... very ugly
hist(main_df$sps_total)
#looks quite a bit better! 
scatterplot(main_df$sps_total,main_df$gfs_current)
#log transform doesn't change correlation much
```

now let's look at cog variables

```{r}
hist(main_df$wrat_standardscore) #looks fine
hist(main_df$bacs_total) #looks fine
hist(main_df$hvlt_total_score) #seems fine for now

scatterplot(main_df$wrat_standardscore, main_df$bacs_total) #wow very little association
scatterplot(main_df$hvlt_total_score, main_df$bacs_total) #better
scatterplot(main_df$hvlt_total_score, main_df$wrat_standardscore) #not great
```

Finally we need to do a bit of recoding of some variables
```{r}
main_df$help_index = main_df$helpful_index #something weird about this variable label
main_df$phenotype_final<-ifelse(main_df$phenotype=="hsc",
                                                  ifelse(main_df$p1_sev>1 | 
                                                         main_df$p2_sev>1 | 
                                                         main_df$p3_sev>1 |
                                                         main_df$p4_sev>1 | 
                                                         main_df$p5_sev>1,
                                                         "hsc_sub","hsc_other"),main_df$phenotype)

main_df$phenotype <- as.factor(main_df$phenotype)
main_df$phenotype_final <- factor(main_df$phenotype_final, 
                                  levels = c('hc','hsc_other','hsc_sub','chr') )
#we want only baseline values 
main_df <- main_df[main_df$visit == 'bl',]

#there is a weird duplicate so let's drop for now
main_df<-main_df[!duplicated(main_df$src_subject_id),]

#let's also drop folks with NA for their phenotype_final (probably due to having NAs on SIPS)
main_df<-main_df[!is.na(main_df$phenotype_final)]

#let's make biological sex numeric and make it zeros and ones
main_df$demo_biological_sex <- as.numeric(main_df$demo_biological_sex)-1

#get rid of folks with negative context sensitivity
main_df$context_sensitivity <- ifelse(main_df$context_sensitivity<0 | 
                                               is.na(main_df$context_sensitivity),
                                               NA,
                                               main_df$context_sensitivity)



#let's also make some plotworthy variable names
main_df$`BACS Total`<-main_df$bacs_total
main_df$`WRAT Standard`<-main_df$wrat_standardscore
main_df$`HVLT Total`<-main_df$hvlt_total_score
main_df$`Global Functioning: Role`<-main_df$gfr_current
main_df$`Global Functioning: Social`<-main_df$gfs_current
main_df$`Social Phobia Scale`<-main_df$sps_total
main_df$`Context Sensitivity`<-main_df$context_sensitivity_all_trials
main_df$`Misleading Index`<-main_df$misleading_index
main_df$`Inverted Faces Reported`<-main_df$inverted_faces_reported
main_df$`Upright Faces Reported`<-main_df$upright_faces_reported
```
let's save out df and create new script since this one is getting long
```{r}
#let's save as .RData file to keep meta-data
save(main_df,file = paste0(main_dir,'RData/cleaned.RData'))
```