---
output:
  pdf_document: default
  html_document: default
---
First question from data request:
1. Does atypical perceptual processing track with reduced cognitive and social functioning?
2. Which social and cognitive functioning variables best predict atypical task performance?
3. Does accounting for cognitive/social functioning significantly reduce group differences?

So atypical perception is:
1. Ebbinghaus -> context_sensitivity, misleading_index, helpful_index (don't know what 2sd is yet)
2. Mooney -> Silverstein's paper from 2021 seems largely focused on upright_percent_reported 
and inverted_percent_reported

Cognitive functioning is: 
1. the Wide Range Achievement Test (WRAT) -> wrat_standardscore
2. the Brief Assessment of Cognition in Schizophrenia-Symbol Coding (BACS) -> bacs_total
3. Hopkins Verbal Learning Test-Revised (HVLT-R) -> hvlt_total_score

Social functioning is Global Functioning Scale:
1. Social and Role (GFS-S/R) -> gfs, gfr
2. Social Phobia Scale ->sps

```{r}
library(data.table)
main_dir = "/Users/victorpokorny/Library/CloudStorage/GoogleDrive-vpokorny123@gmail.com/My Drive/CAPR Ebbinghaus and Mooney/"
source(paste0(main_dir,'R_scripts/funcs.R')) # big group of functions
load(file=paste0(main_dir,"RData/cleaned.RData")) #read in the data
#subset to only CHR
main_df<-main_df[main_df$phenotype_final=='chr',]
```
1. Does atypical perceptual processing track with reduced cognitive and social functioning?
```{r}
#context sensitivity and cognition
#let's look at bivariate associations first
perception_variables = c('context_sensitivity_all_trials')
cognition_variables = c('bacs_total', 'wrat_standardscore','hvlt_total_score')
p_vals = NULL
combo_names = NULL
for (j in perception_variables){
  for (jj in cognition_variables){
    res = cor.test(main_df[[j]], main_df[[jj]])
    combo_name = paste(j,jj)
    combo_names = rbind(combo_names,combo_name)
    print(combo_name)
    print(pub_ready_stats(res))
    p_val = res$p.value
    p_vals = rbind(p_vals,p_val)
  }
}
cbind(unname(combo_names), round(p.adjust(p_vals, 'fdr'),3))

#then multivariate prediction
summary(lm(context_sensitivity ~ wrat_standardscore + bacs_total + hvlt_total_score +nocontext_sizediffother_perc_acc, main_df))
pub_ready_stats(lm(context_sensitivity ~ wrat_standardscore + bacs_total + hvlt_total_score, main_df))

#context sensitivity and social/role
cognition_variables = c('gfs_current', 'gfr_current','sps_total')
p_vals = NULL
combo_names = NULL
for (j in perception_variables){
  for (jj in cognition_variables){
    res = cor.test(main_df[[j]], main_df[[jj]])
    combo_name = paste(j,jj)
    combo_names = rbind(combo_names,combo_name)
    print(combo_name)
    print(pub_ready_stats(res))
    p_val = res$p.value
    p_vals = rbind(p_vals,p_val)
  }
}
cbind(unname(combo_names), round(p.adjust(p_vals, 'fdr'),3))
```

```{r}
#now mooney faces bivariate associations
mooney_variables = c('inverted_faces_reported')
cognition_variables = c('bacs_total', 'wrat_standardscore','hvlt_total_score')
p_vals = NULL
combo_names = NULL
for (j in mooney_variables){
  for (jj in cognition_variables){
    res = cor.test(main_df[[j]], main_df[[jj]])
    combo_name = paste(j,jj)
    combo_names = rbind(combo_names,combo_name)
    print(combo_name)
    print(pub_ready_stats(res))
    p_val = res$p.value
    p_vals = rbind(p_vals,p_val)
  }
}
cbind(unname(combo_names), round(p.adjust(p_vals, 'fdr'),3))

cognition_variables = c('gfs_current', 'gfr_current','sps_total')
p_vals = NULL
combo_names = NULL
for (j in mooney_variables){
  for (jj in cognition_variables){
    res = cor.test(main_df[[j]], main_df[[jj]])
    combo_name = paste(j,jj)
    combo_names = rbind(combo_names,combo_name)
    print(combo_name)
    print(pub_ready_stats(res))
    p_val = res$p.value
    p_vals = rbind(p_vals,p_val)
  }
}
cbind(unname(combo_names), round(p.adjust(p_vals, 'fdr'),3))

#multiple regression
pub_ready_stats(lm(inverted_faces_reported ~ gfs_current+gfr_current+sps_total, main_df))

```

